---
title: "Final-project-draft"
author: "Nassangnan Kamagate"
date: "5/11/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Intro

In this project,! will gain insight  into public  health by generating simple graphical and  numerical summaries of a data set collected by the collected from different hospitals , community clinics, maternal health cares through the IoT based risk monitoring system.

## What

I would  like to  determine  the  risk level of  pregnant  women of 18  and less.  To help  me,i will be  using a data set from Kaggle.

## Why

It is important to know if  they are on high  risk level so that  we can  make some sensitization  and  also work on how to find some solution to protect them and fight against those condition

## How

I will use R Markdown to determine the rate. I would like to go further by determining Which  health conditions are the strongest indications for health risks during pregnancy?


# Body

The purpose of this will the be  to  analyse and  calculate the  risk level faced  by pregnant  women  under the age of 18  and know  which  category  of  the  conditions  affect  them  the  most . By  doing  this study  we can learn and try to protect their pregnancy  .The differ e nt attributes are :  Systolic BP: Upp er  value of  Blood Pressure in mmHg, another significant attribute during pregnancy. 

Diastolic BP: Lower  value of Blood Pressure in  mmHg,  another  significant  attribute  during  pregnancy.  

BS: Blood  glucose  levels is in terms of a molar concentration, mmol/ L. Heart Rate: A normal resting heart rate in beats per minute . 

Risk Level: Predicted Risk Intensity Level during pregnancy considering the previous attribute.

## study of the Data

```{r}
library(readxl)
setwd('C:/Users/kamag/Downloads/')
MAT <- read_excel("MAT.xlsx")
library(Hmisc)
describe(MAT)


```

In this that data we have 7 variable for 1014 Oobservation


## Distribution of Risk Level

```{r}
table(MAT$RiskLevel)
```

We know from the distribution that most of the pregnant women have A low risk conditions .

```{r}
RiskLevel <- table(MAT$RiskLevel)
plot(as.factor(MAT$RiskLevel),MAT$HeartRate)
```

```{r}
anova(aov(HeartRate ~ RiskLevel, data=MAT))
```



```{r}
head(MAT)
```

```{r}
tail(MAT)
```

## Pregnant  women under 18

```{r}
table(MAT$Age<18)
```

```{r}
Age <- table(MAT$Age<18) 
barplot(Age)
```

## Pregnant women under 18 with high risk level

```{r}
ltage18 <- subset(MAT, Age<18) 
ltage18
```

```{r}
MAT$RiskLevel == "high risk"
```

```{r}
hr <- MAT$RiskLevel == "high risk"
hr <- subset(MAT, MAT$RiskLevel == "high risk")
p18_highrisk <- subset(ltage18, ltage18$RiskLevel == "high risk")

```

From the research above we can see that 37 seven person out 272 from the list of women under 18 are in high risk . This represent 13% of the list . It's a small percentage but it is still not to be be neglected.

## Study of the different condition

## DiastolicBP

```{r}
summary(MAT$DiastolicBP)
```

## systolicBP

```{r}
summary(MAT$SystolicBP)
```

## BS

```{r}
summary(MAT$BS)
```

## Heart Rate

```{r}
summary(MAT$HeartRate)
```


# Topics From Class

## Rmarkdown:

One of my favorite things to  use this semester,  it is my first semester  in Business  Analytics I was scared at the beginning but really after having one class I really loved it.

## Github:

This is an also something I enjoy learning I did not go yet as far I wanted to  go for  now  but  I  will like to learn more about it. ## HMISC  package:  I used the  package  hmisc to describe the  Data have and  more incite of the Data.

## Anova:

I used this topics from the suggestion of one of  the  student  and it came out  great.  It really help me have create a great visualisation .
 
## Data subsetting:

This one of my favorite I really enjoy using it  in my homeworks so I decide to  use it for my project and it really me acheive what I was looking for.


# Conclusion

This project help me learn a lot , it help me surpass myself and succeed my research. It help me learn new function also go back  to  what  I learned in class and  study them more.  It  help me advance my knowledge This is my first semester  ,I was scared  at  beginning  but  i learned  that  nothing  is too  hard or too easy we just have be ready to work harder.


# Citation:

HMISC: Donovan, K. (2019, July 11). Data Analysis and processing with R based on Ibis Data. 9 Docu­ menting your results with R Markdown. Retrieved May 8, 2022, from  
https://bookdown.org/kdonovan125/ ibis_data_analysis_ r4/ documenting-your-results-with- r-markdown.html


